---
title: "Data and Methods"
---

The source of the following data analysis is from New York City crime dataset available online. The data used specifically is Murder rates by precinct in the year of 2010. The data for all other vairables analyzed is for the year 2011. The data below is broken down by variable for the overall year. 

Variable analyzed from the year 2010, 

**Overall Murder rates**

```{r}
hist(MurderRates2010ALLPCT)
```

Variables analyzed from the year 2011 are as follows, 

* Frisked (Y/N)*
* Sex (M/F/Z)*
* Race (Asian, Black, White, etc.)*
* Age 

The units of analysis for this project are by precinct for murder rates, frisked, sex, race, and age. 

Below is the r code for each variable tested in correlation with murder rates. 

**Overall Race Breakdown**

Race                    |  Percentage 
---------               | -----------
Asian                   | 3.5% 
Black                   | 51.1%
Indian                  | > 1% 
Pacific Islanders       | 7.1%
Q                       | 25.6%
U                       | > 1%
White                   | 9% 
Z(Not Stated)           | 2.4%

```{r}
barplot(RacePlot)
``` 

**Overall Sex Breakdown**

Sex           |  Percentage
-----         | -----------
Male          | 91.1% 
Female        | 6.8%
Z(Not Stated) | 1.8% 

```{r}
barplot(GenderPlot)
```

**Overall Frisked Breakdown**

Frisked   |  Percentage
-----     | -----------
Yes       | 55.7% 
No        | 44.3%

```{r}
barplot(FriskedPlot)
```



The data posted below is each varibale by New York City Police Precinct.

*KEY: 

* Frisked: Y-yes; N-no
* Sex: M-male; F-female; Z- Not available 
* Race: A- Asian; B- Black; I- Indian; P- ; Q- ; U- ; W- White; Z- Not avialable
* Age: By number 